Autoignition of Methyl Valerate at Low to Intermediate Temperatures and Elevated Pressures in a Rapid Compression Machine

### 2017-06-27 methyl-valerate.tex
Updates

To the best of our knowledge, there are three mechanisms for MV combustion available in the
literature. The first two, by \cite{Korobeinichev2015} and \cite{Dmitriev2015}, were developed to
simulate flames, and do not include the low-temperature chemistry necessary to simulate the
conditions in these experiments. The third model was developed by \cite{Dievart2013} and includes
low-temperature chemistry of MV, although it was only validated by comparison with flame extinction
limits. In converting this mechanism for use in Cantera, we found that there were many species in the
thermodynamic database with multiple data entries. For most of these species the thermodynamic data
is identical. However, some species are not exact duplicates. For these species, it is not clear
from the thermodynamic database file which data set should be preferred. Since Cantera (and CHEMKIN)
choose the first instance of a duplicate species to be used, we retained the first entry for all
duplicated species. The detailed \cite{Dievart2013} model includes \todo{check this}1103 species and 7557 reactions,
and the CHEMKIN and Cantera formatted input files are available in the Supplementary Material.

@@

In addition to using a mechanism from the literature, we investigate the use of an automatic
mechanism generator, the open-source Reaction Mechanism Generator (RMG)~\cite{Allen2012} version
2.1.0. The Python version of RMG is used, which requires Python 2.7, and version 2.1.0 of the RMG
database is used. The final RMG model contains 483 species and 19990 reactions. Note that the number
of species is much lower than the \cite{Dievart2013} model because the RMG model focuses on only one
fuel (MV), but the number of reactions is substantially higher. The input file used to generate the
model is available in the Supplementary Material.

>>>>

To the best of our knowledge, there are three mechanisms for MV combustion available in the
literature. The first two, by \cite{Korobeinichev2015} and \cite{Dmitriev2015}, were developed to
simulate flames, and do not include the low-temperature chemistry necessary to simulate the
conditions in these experiments. The third model was developed by \cite{Dievart2013} and includes
low-temperature chemistry of MV, although it was only validated by comparison with flame extinction
limits. In converting this mechanism for use in Cantera, we found that there were many species in the
thermodynamic database with multiple data entries. For most of these species the thermodynamic data
is identical. However, some species are not exact duplicates. For these species, it is not clear
from the thermodynamic database file which data set should be preferred. Since Cantera (and CHEMKIN)
choose the first instance of a duplicate species to be used, we retained the first entry for all
duplicated species. The detailed \cite{Dievart2013} model includes 1105 species and 7141 reactions,
and the CHEMKIN and Cantera formatted input files are available in the Supplementary Material.

@@

In addition to using a mechanism from the literature, we investigate the use of an automatic
mechanism generator, the open-source Reaction Mechanism Generator (RMG)~\cite{Allen2012} version
2.1.0. The Python version of RMG is used, which requires Python 2.7, and version 2.1.0 of the RMG
database is used. The final RMG model contains 427 species and 13640 reactions. Note that the number
of species is much lower than the \citet{Dievart2013} model because the RMG model focuses on only
one fuel (MV), but the number of reactions is substantially higher. The input file used to generate
the model is available in the Supplementary Material.
